Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
how's this
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60877 72bbbca6-d526-0410-a7d9-f06f51895060

%%%%% Stuff for this paper %%%%%
\usepackage{tikz-dependency}
\newcommand{\gmk}[1]{\texttt{#1}}
\newcommand{\gloss}[1]{#1}
\newcommand{\tag}[1]{\texttt{‹#1›}}
\newcommand{\udtag}[1]{\texttt{@#1}}
\newcommand{\udlabel}[1]{{\udfont #1}}
%\newcommand{\corrauthor}[1]{\footnotemark\footnotetext{hargle}}

@@

As seen in the graphs, the compound relationship of an attributive nominal depending on another nominal is labelled \udlabel{compound}, and genitive relations are considered \udtag{nmod}, regardless of whether there is a definite or indefinite genitive construction.

>>>>

%%%%% Stuff for this paper %%%%%
\usepackage{tikz-dependency}
\newcommand{\gmk}[1]{\texttt{#1}}
\newcommand{\gloss}[1]{#1}
\newcommand{\tag}[1]{\texttt{‹#1›}}
%\newcommand{\udtag}[1]{\texttt{@#1}}
\newcommand{\udtag}[1]{\textsc{\texttt{#1}}}
\newcommand{\udlabel}[1]{{\udfont #1}}
%\newcommand{\corrauthor}[1]{\footnotemark\footnotetext{hargle}}

@@

As seen in the graphs, the compound relationship of an attributive nominal depending on another nominal is labelled \udtag{compound}, and genitive relations are considered \udtag{nmod}, regardless of whether there is a definite or indefinite genitive construction.
